The emotion--facial expression link: Evidence from human and automatic expression recognition

### 2020-11-04 manuscript/manuscript_apa.Rmd
acknowledgment

wordcount         : "7943"
bibliography      : ["bib/manuscript_ref.bib"]
csl               : ["csl/apa7.csl"]

@@

output: papaja::apa6_word

# output            :
#   bookdown::pdf_book:
#     toc: false
#     number_sections: false
#     base_format: papaja::apa6_pdf

@@

>>>>

wordcount         : "8558"
bibliography      : ["bib/manuscript_ref.bib", "bib/r-references.bib"]
csl               : ["csl/apa7.csl"]

@@

#output           : papaja::apa6_word

output            : 
  bookdown::pdf_book:
    toc: false
    number_sections: false
    base_format: papaja::apa6_pdf

@@

# Acknowledgement

The authors would like to thank the developers of the following R packages used to process, analyze, display and report data: `r papaja::cite_r(file = "bib/r-references.bib")`.

# Data availability

The R code and relevant data for statistical computing are available on the "The emotion–facial expression link (data and code)" repository from the Center for Open Science [@Dupré_Tcherkassof_2020].
